Evaluating Model Performances

### 2019-04-09 Scripts/evaluating_model_performances.Rmd
editted results scripts

>>>>

## Plots

#GM12878
c <- ggplot(all_rfperfs[which(all_rfperfs$CL=="GM12878" & all_rfperfs$Predictor=="OC" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
     geom_line(size=2)+
     geom_point(size=5)+
     facet_grid(~ Metric)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("") + ylim(-.05,.5) +
     ggtitle("Overlap Counts") +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

p <- ggplot(all_rfperfs[which(all_rfperfs$CL=="GM12878" & all_rfperfs$Predictor=="OP" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
     geom_line(size=2)+
     geom_point(size=5)+
     facet_grid(~ Metric)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("") + ylim(-.05,.5) +
     ggtitle("Overlap Percents") +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

d <- ggplot(all_rfperfs[which(all_rfperfs$CL=="GM12878" & all_rfperfs$Predictor=="Distance" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
     geom_line(size=2)+
     geom_point(size=5)+
     facet_grid(~ Metric)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("") + ylim(-.05,.5) +
     ggtitle("Distance") +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

#K562
c2 <- ggplot(all_rfperfs[which(all_rfperfs$CL=="K562" & all_rfperfs$Predictor=="OC" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
     geom_line(size=2)+
     geom_point(size=5)+
     facet_grid(~ Metric)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("") + ylim(-.05,.5) +
     ggtitle("Overlap Counts") +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

p2 <- ggplot(all_rfperfs[which(all_rfperfs$CL=="K562" & all_rfperfs$Predictor=="OP" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
     geom_line(size=2)+
     geom_point(size=5)+
     facet_grid(~ Metric)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("") + ylim(-.05,.5) +
     ggtitle("Overlap Percents") +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

d2 <- ggplot(all_rfperfs[which(all_rfperfs$CL=="K562" & all_rfperfs$Predictor=="Distance" & (all_rfperfs$Metric=="F1-Score" | all_rfperfs$Metric=="MCC")),], aes(x=Resolution, y=Performance, color=Resampling, group=Resampling)) +
     geom_line(size=2)+
     geom_point(size=5)+
     facet_grid(~ Metric)+
     theme_minimal() +
     theme_bw()+
     xlab("") + ylab("") + ylim(-.05,.5) +
     ggtitle("Distance") +
     scale_color_discrete(name="Resampling Technique")+
     guides(shape=FALSE, linetype=FALSE)+
     theme(axis.text.x = element_text(size=15,
                                      angle = 45, 
                                      #margin = ggplot2::margin(t = 35),
                                      hjust = 1
     ),
     axis.text.y = element_text(size = 15),
     axis.title.x = element_text(size = 20),
     axis.title.y = element_text(size = 20),
     legend.text=element_text(size=15),
     legend.title=element_text(size=20),
     plot.title = element_text(size=20))

figure <- ggarrange(c2,p2,d2,
                ncol = 3, nrow = 1, 
                common.legend = TRUE, 
                legend = "top",
                labels = "AUTO",
                font.label = list(size=20))
figure
annotate_figure(figure,
    bottom = text_grob("Resolution", color = "black", size = 20),
    left = text_grob("Performance", color = "black", rot = 90, size=20)
)

figure <- ggarrange(c,p,d,c2,p2,d2,
                ncol = 3, nrow = 2, 
                common.legend = TRUE, 
                legend = "top")
figure
annotate_figure(figure,
    bottom = text_grob("Resolution", color = "black", size = 20),
    left = text_grob("Performance", color = "black", rot = 90, size=20)
)
